---
title: Spark NorthWest 3G Shutdown Data
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: "Segoe UI", sans-serif;
  line-height: 1.6;
  margin: 20px;
}

h2 {
  color: #6026a0;
  border-bottom: 2px solid #6026a0;
  padding-bottom: 5px;
}

p {
  font-size: 16px;
}

img {
  max-width: 100%;
  border-radius: 16px;
}

.chart-title {
  font-weight: bold;
  color: #6026a0;
}
```

## What are Spark NorthWest customers doing about the 3G shutdown?
This dynamic report analyzes the behavior of customers at Spark NorthWest during the 3G shutdown transition. 

The data includes customer age ranges, device types, upgrade decisions, and staff ratings of Spark’s performance. The visualisations below summarise key patterns in the observations collected.



```{r}
library(tidyverse)
# URL for the Google sheet published as a CSV and assigning it to logged_data
logged_data <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vR7hXOK9yfyx-RxWw31m0r4blZ4quf19kEsSE16WkpTIttuX79yGV0U2nSYPivzCPRYg6QDomSB6SdM/pub?output=csv"
# Using the read_csv() function to read the data
# into a data frame named logged_data
logged_data <- read_csv(logged_data)
# Using the rename() function to read the data into a data frame names logged_data
latest_data <- logged_data %>%
  rename(date_of_shift = 2,
         customers_age_range = 3, 
         did_customer_upgrade_device = 4,
         customers_device_type = 5,
         upgraded_device_type = 6,
         spark3g_offer = 7,
         customers_feeling = 8,
         device_status = 9,
         roaming_upgrade = 10,
         spark3g_shutdown_rating = 11)

#finding the minimum age range of customers that have come into Spark NorthWest store

#finding the maximum age range of customers that have come into Spark NorthWest store to query about the 3G network shutdown and embedding it into a statement

#finding the average rating of what the Spark NorthWest staff think about how well Spark is doing regards the change from 3G network to 4G and embedding it into a statement
average_rating <- mean(latest_data$spark3g_shutdown_rating, na.rm = TRUE) %>% round(1)
```

The youngest age range that came in the Spark NorthWest store to query about the 3G shutdown is `r min(latest_data$customers_age_range)`.  
The oldest age range came in the Spark NorthWest store to query about the 3G shutdown is `r max(latest_data$customers_age_range)`.  
The average staff rating for Spark’s handling of the 3G shutdown was `r average_rating`. This reflects Spark NorthWest staff’s view of how well Spark NZ is managing the transition from 3G network to 4G/5G network.



```{r}
#making a plot to show the ratings of Spark NorthWest staffs thoughts on 3G network shutdown
#first putting more appropriate variable name for the rating otherwise on the graph it will just display latest_data$spark3g_shutdown_rating
customer_device_type <- latest_data$customers_device_type
customer_age_range <- latest_data$customers_age_range
latest_data %>%
  ggplot() + 
  #setting x axis as the rating of staff and filling in whether the customer upgraded or not, below that setting appropriate labels for title, subtitle, x axis name, y axis name
  geom_bar(aes(x = did_customer_upgrade_device, fill = customer_age_range)) + 
  labs(title = "Did Customer Have To Upgrade their Device?",
       subtitle = "Did customers have to upgrade their device? And what age range?",
       x = "Did Customer Have To Upgrade? (Yes or No)",
       y = "Number Of Customers")


#making a plot to show the ratings of Spark NorthWest staffs thoughts on 3G network shutdown
#first putting more appropriate variable name for the rating otherwise on the graph it will just display latest_data$spark3g_shutdown_rating
customer_device_type <- latest_data$customers_device_type
customer_upgrade_device <- latest_data$did_customer_upgrade_device
latest_data %>%
  ggplot() + 
  #setting x axis as the rating of staff and filling in whether the customer upgraded or not, below that setting appropriate labels for title, subtitle, x axis name, y axis name
  geom_bar(aes(x = customer_upgrade_device, fill = customer_device_type)) + 
  labs(title = "Did Customers Have To Upgrade Device?",
       subtitle = "Did customers have to upgrade their device? What current device do they have currently?",
       x = "Did Customer Have To Upgrade? (Yes or No)",
       y = "Number Of Customers")


#making new data frame without NA values (blank answers) for whether customer had button phone or smartphone and the blank answers for what device customer upgraded to because both of those questions were conditional questions
#remove NA values from customers device type data in latest_data
removingna_customers_device_type <- !is.na(latest_data$customers_device_type)
#remove NA values from customers upgraded device type data in latest_data
removingna_upgraded_device_type <- !is.na(latest_data$upgraded_device_type)
#creating updated rows of those removed NA values 
rows_without_na <- removingna_customers_device_type & removingna_upgraded_device_type
#creating updated columns of those removed NA values 
columns_without_na <- c("customers_device_type", "upgraded_device_type")
#putting those rows and columns into data frame new_data
new_data <- latest_data[rows_without_na, columns_without_na]

#making a plot to show the what kind of devices the button phone people have upgraded to and the smart phone people have upgraded to
#first putting more appropriate variable name for the customers current device type otherwise on the graph it will just display new_data$customers_device_type
#putting more appropriate variable name for the customers upgraded device otherwise on the graph it will just display new_data$upgraded_device_type
customer_current_device <- new_data$customers_device_type
customer_upgraded_device <- new_data$upgraded_device_type
ggplot() + 
  #setting x axis as what device type the customer currently has, filling it in with what device they have upgraded to, below that setting appropriate labels for title, subtitle, x axis name, y axis name
  geom_bar(aes(x = customer_current_device, fill = customer_upgraded_device)) + 
  labs(title = "What Kind Of Devices Were Bought The Most?",
       subtitle = "For the customers who had to upgrade from a 3G to a 4G/5G device, what kind of device did they upgrade to?",
       x = "Customers Current Device",
       y = "Number Of Customers")



#making a plot to show the ratings of Spark NorthWest staffs thoughts on 3G network shutdown
#first putting more appropriate variable name for the rating otherwise on the graph it will just display latest_data$spark3g_shutdown_rating
sparknorthwest_staff_rating <- latest_data$spark3g_shutdown_rating
latest_data %>%
  ggplot() +
  #setting y axis as the rating of staff and setting bar colours to purple, below that setting appropriate labels for title, subtitle, x axis name, y axis name
  geom_bar(aes(y = sparknorthwest_staff_rating),
           fill = "#6026a0") +
  labs(title = "Spark NorthWest Staff Rating",
       subtitle = "Spark NorthWest staff's ratings on how good of a job Spark NZ is doing in regards to 3G network shutdown on a scale of 1-10",
       x = "Rating",
       y = "Number Of Responses")

```










